---
title: "`r params$title`"
author: "`r params$author`"
date: "`r params$date`"
---

```{r setup, include=FALSE}
library(knitr)
#opts_chunk$set(cache=TRUE, echo = FALSE, fig.width=7, fig.height=7)
#knit_hooks$set(optipng = hook_optipng)
# output: html_document
knitr::opts_chunk$set(echo = FALSE, fig.width=7, fig.height=7)
#knitr::knit_hooks$set(optipng = hook_optipng)
# knitr::opts_chunk$set(dev = 'pdf')
knitr::opts_chunk$set(dev = 'jpeg')

# Options
path_main <- params$path_main 
project_id <- params$project_id
pred_file <- paste(params$model_id,"_",params$ts_id,"_preds_val",sep="")
log_file <- paste(params$model_id,"_",params$ts_id,"_training",sep="")
model <- params$model_id
project_name <- params$project_name
subject_set <- paste("val_subject_set_",params$model_id,sep="")
n_classes <- params$n_classes

# fig.height=width_large, fig.width=width_large
width_large <- 12
height_large <- 12
height_very_large <- 18

# fig.height=width_med, fig.width=width_med
width_med <- 10
height_med <- 10

# fig.height=width_small, fig.width=width_small
width_small <- 6
height_small <- 6

width_variable <- width_small + min(n_classes/width_small, width_small)
height_variable <- height_small + min(n_classes/height_small, width_small)


```


```{r, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
############################ -
# Libraries ----
############################ -

library(ggplot2)
library(reshape2)
library(plyr)
library(dplyr)
library(jsonlite)
library(jpeg)
library(grid)
library(gridExtra)

# source("analyses/plot_functions.R")
# 
# # Load Functions
# source("analyses/plot_functions.R")
# 
# # Load data
# source("analyses/load_data.R")
```

## Introduction

This report shows results obtained from training and evaluating a convolutional neural network (CNN) using images from `r params$project_name`. The goal is to automatically identify different types of camera-trap images. 

The data has been divided into a training, a validation and a test set. The model has only seen the training set, while the validation set was used to monitor the model during training time. The test set is only used to report final results (this report is not final, hence contains results from the validation set). For each image the model estimates probabilities for each class/species (values between 0 and 1, while the sum over all classes is 1). To each image we assign the class with the highest output value.

The labels from which the CNN learns from have been obtained by annotations of users on Zooniverse. We have used the plurality algorithm to assign labels to individual camera-trap events. Whenever most users think there is only one species in an image (median number of species is 1), we have assigned the most frequent annotation as class label. Images where most users have identified multiple species have been excluded to reduce complexity in the training process. The number of annotations per image can vary significantly, in extreme cases only 1 person might have annotated an image. Where available, the retirement reason as defined by the project logic has been used to generate labels (e.g. if an image was retired early because of annotations indicating an empty image).
\newpage

## Overview

### Correct Predictions

Shown are some randomly selected correct classifications.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=height_very_large, fig.width=width_large}

############################ -
# Find some correct classifications ----
############################ -

random_wrongs <- dplyr::filter(preds,correct==1)
set.seed(23)
random_wrongs <- random_wrongs[sample(size = 10,x=dim(random_wrongs)[1]),]

gg <- plot_subject_image_set(pred_set=random_wrongs, subjects, path_scratch, n_samples=dim(random_wrongs)[1], ncol=2, nrow=5)
gg

############################ -
# Plot correct classifications ----
############################ -

# for (ii in 1:10){
#   id <- paste(random_wrongs[ii,"subject_id"])
#   preds_sel <- random_wrongs[ii,"preds_all"]
#   gg <- plot_subject_image(preds_sel, subjects, id, path_scratch, ii)
#   print_name = paste(path_figures,model,"_sample_wrong_",ii,sep="")
#   #grid.arrange(gg1,gg2,top=title)
#   grid.draw(gg[[1]])
#   grid.draw(gg[[2]])
#   grid.newpage()
# }

```



```



